% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Yifan Cai}

\basicInfo{
  \email{fyc1007261@live.com} \textperiodcentered\ 
  \phone{(+86) 13857154817} \textperiodcentered\ 
  \github[fyc1007261]{https://github.com/fyc1007261}}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Shanghai Jiao Tong University (SJTU)}, Shanghai, China}{2016 -- Present}
\textit{Bachelor} in Software Engineering
\begin{itemize}
  \item Overall GPA: 3.73 / 4.30 (87.75 / 100)
  \item Major GPA: 3.89 / 4.30 (90.53 / 100)
\end{itemize}

\section{\faUsers\ Experience}
\datedsubsection{\textbf{University of Michigan at Ann Arbor} Michigan, U.S.}{July 2018 -- August 2018}
\role{Research Assistant}{Advisor: Prof. Xianglei Huang}
Brief introduction: Built a LSTM-based solar forecasting system on keras framework, in python language. The result, in specific conditions, is better than all of those in published papers.
\begin{itemize}
  \item Wriiten in Python
  \item Able to run both on Linux and Windows
  \item A very high accuracy
\end{itemize}


\datedsubsection{\textbf{Electric Appliance Monitoring and Scheduling System}}{July 2018}
\role{Full Stack}{Group Project}
Brief introduction: Collaboratively built an electric appliance monitoring and scheduling system. I mainly focused on the back-end (in Java) of the web application, and the integrated hardware controlling system, which collects all information from the sensors and operates the appliances.
\begin{itemize}
  \item Written in JavaScript, Java, SQL, Python, and Matlab
  \item Cross-process communications 
  \item Smart scheduling for appliances considering renewable energy
  \item Deep learning based solar energy forecasting (which is improved then in August)
  \item Convenient human computer interaction (audio, gesture, body, etc.)
\end{itemize}

\datedsubsection{\textbf{HikVision} Hangzhou, China}{Februray 2018}
\role{Winter Intern}

Brief introduction: Had an internship at HikVision, a computer vision company. Helped improve demos of the monitoring system.
\begin{itemize}
  \item Written in C++
  \item Got familiar with Windows interfaces
  \item Improved the program with multi-threading and socket communications
\end{itemize}


\datedsubsection{\textbf{Basic B+ Tree Based Database}}{July 2017 - August 2018}
{Individual Project}
Brief introduction: Designed a B+ tree based database system. The system supports CRUD operations. 
\begin{itemize}
  \item Written in C++
  \item Cache system between disk and memory
  \item High performance when running with over 1,000,000 sets of data.
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: Python, C/C++, Java, JavaScript, etc.
  \item Development: Web, Deep Learning Model, etc.
  \item Languages: English (TOEFL 104), Mandarin Chinese (Native)
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
